---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pytt

<!-- badges: start -->
[![R-CMD-check](https://github.com/GilHenriques/pytt/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/GilHenriques/pytt/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

**Pyttipanna** is a Swedish dish made by mixing together small bits and pieces 
of leftover food. The word means "small bits in a pan". Much like a pyttipanna,
`{pytt}` is a collection of bits and pieces thrown together. It includes very
simple utility functions that I use commonly. Most functions in `{pytt}` are
simply wrappers around other functions. 

## Installation

You can install pytt from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("GilHenriques/pytt")
```

## Functions included in `{pytt}`

### Binary operators

The package includes a series of binary operators that manipulate strings. 
These are wrappers around the base functions `paste0`, `grepl`, and `substr`:

```{r example, echo=TRUE}
library(pytt)

# Paste operator (`paste0`):
pytt_i_panna <- 'pytt i panna'
'Pyttipanna is also called ' %_% pytt_i_panna

# Pattern-matching operator (`grepl`):
c('Pytt i panna', 'Pyttipanna') %like% '\\s'

# Substring (first or last few characters) operator (`substr`):
pytt_i_panna %left% 6
pytt_i_panna %right% 2
```

Some binary operators are not specific to strings:

```{r example2, echo=TRUE}
library(pytt)

# Negated %in% operator:
1:3 %!in% 3:5
```
